### 2023-03-07 glossaries/links.tex
Fix citations in article
Numbers in old style
and others typographic checks

@@

\newlink{epsg-chl}{\texttt{EPSG:32662}}{https://epsg.io/32662}
\newlink{epsg-sst}{\texttt{EPSG:4326}}{https://epsg.io/4326}

>>>>

\newlink{biogeosciences}{Biogeosciences}{https://www.biogeosciences.net/}
\newlink{preprint-bgs}{Pre-print}{https://egusphere.copernicus.org/preprints/2023/egusphere-2022-1489/}
\newdoi{preprint-bgs-doi}{Pre-print}{10.5194/egusphere-2022-1489}

@@

\newlink{epsg-chl}{EPSG:32662}{https://epsg.io/32662}
\newlink{epsg-sst}{EPSG:4326}{https://epsg.io/4326}
